Title

### 2020-03-13 article/parts/04_user_notes.tex

\section{User notes}
By accessing the APP users can filter and download the resulting data sets as a comma-separated values (csv) file. Users of the R-package can directly load the data in R. The R-package provides the two functions \textit{stx\_catalog()} and \textit{stx\_query()}. The first queries a catalog of possible Standartox parameters into a R list object. The latter allows users to set the Standartox filter parameters and to fetch the actual data. It returns a R list of three tables (i.e. R data.frames) containing the filtered data set, the aggregated data set and a table with the meta information retrieved from the API endpoints \textit{/filter} and \textit{/meta}. A short R-code example is given below \ref{lis:standartox-example} and a detailed description on the usage of the R package is provided on its Github page: \url{https://github.com/andschar/standartox}.

>>>>

\section{User notes}
By accessing the web application users can filter and download the resulting data sets as a comma-separated values (csv) file. Users of the R-package can directly load the data in R. The R-package provides the two functions \textit{stx\_catalog()} and \textit{stx\_query()}. The first command queries a catalog of possible Standartox parameters into a R list object. The latter allows users to set the Standartox filter parameters and to fetch the actual data. It returns a R list of three tables (i.e. R data.frames) containing the filtered data set, the aggregated data set and a table with the meta information retrieved from the API endpoints \textit{/filter} and \textit{/meta}. A short R-code example is given below \ref{lis:standartox-example} and a detailed description on the usage of the R package is provided on its Github page: \url{https://github.com/andschar/standartox}.
